Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-11 paper.tex
Rough outline for single origin Pango

>>>>

\begin{figure}
\begin{tabular}{cc}
\includegraphics[width=0.4\textwidth]{figures/Pango_XA_nxcld_tight_graph.pdf}
&
\begin{tabular}{llr}
Lineage & number of samples & other details... \\
XA & & \\
XF & & \\
XG & & \\
XH & & \\
XL & & \\
XR & & \\
XT & & \\
XW & & \\
XY & & \\
XAC & & \\
XAE & & \\
XAK & & \\
\end{tabular}
\end{tabular}
\caption{A. Subgraph for XA (wide ARG). B. Details for the the single-origin Pango
X lineages in the long ARG.}
\end{figure}
